---
title: "Docker Images for Tidylab Packages and Projects"
bibliography: []
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

```{r, error=TRUE}
stop("This article documents functionality that is out of scope for the package version hosted on CRAN.")
```

## Building Docker Images

Build a specific docker image by running

    .Rprofile$docker$start(<service-name>)

The available services are

| Service Name     | Description                                                             |
|------------------|-------------------------------------------------------------------------|
| `r-package`      | Docker image for building R packages.                                   |
| `r-project`      | Docker image for building R projects.                                   |
| `r-ml`           | Docker image for building machine learning in R.                        |
| `r-book`         | Docker image for authoring books in R.                                  |
| `r-microservice` | Docker image for deploying microservices in R.                          |
| `r-stanverse`    | Docker image for developing [Stan](https://mc-stan.org/)-based projects |

For example, to build the `r-package` service run

    .Rprofile$docker$start("r-package")

## Pushing Docker Images to Docker Repository

You can see the available `tidylab` images on [Docker
Hub](https://hub.docker.com/orgs/tidylab/repositories).
